Locus Statistics

### 2017-06-30 doc/RMD/locus-stats.Rmd
wrap session info in details tag

```{r}
library("tidyverse")
library("poppr")
load(file.path(PROJHOME, "data", "sclerotinia_16_loci.rda"))
```

@@

## Session Information

```{r session_info}
options(width = 100)
devtools::session_info()
```

>>>>

```{r load_packages, message = FALSE, warning = FALSE}
library("tidyverse")
library("poppr")
load(file.path(PROJHOME, "data", "sclerotinia_16_loci.rda"))
```

@@

<details>
<summary>Session Information</summary>

```{r, echo = FALSE}
options(width = 100)
devtools::session_info()
```

</details>
